---
title: "How to work with images"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How to work with images}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{r setup}
library(panstarrs)
library(magick)
```

# Example 1

## Plot color image of the Antennae galaxies

```{r}
coords_antennae <- ps1_mast_resolve('Antennae')

ps1_image_color(
  coords_antennae$ra, 
  coords_antennae$dec, 
  format = 'png', 
  size = 600
) |> 
  magick::image_read() |> 
  magick::image_resize("400x400")
```

# Example 2 

## Making guidance picture

### 1. Get coords of the KQ Uma

```{r}
coords_uma <- ps1_mast_resolve('KQ Uma')
coords_uma
```

```{r}
img_url <- ps1_image_url(
  coords_uma$ra, 
  coords_uma$dec, 
  size = 1280, 
  filter = "r", 
  format = "fits"
)
fits_obj <- FITSio::readFITS(img_url)
```

### 2. Fix header

FITS image headers use the obsolete PC001001, PC001002, etc., keywords for the WCS. We should fix (add some keywords to headers) it to plot right using magicaxis package

```{r}
fix_header <- function(header) {
  # FITSio --> obj$hdr

  is_header_ok <- any(grepl("CD1_1", header))

  if (is_header_ok) {
    return(header)
  } else {
    PC001001 <- header[which(header == "PC001001") + 1] |> as.numeric()
    CDELT1 <- header[which(header == "CDELT1") + 1] |>as.numeric()
    CD1_1 <- (PC001001 * CDELT1) |> sprintf(fmt = "%.14e")


    CD1_2 <- "0"
    CD2_1 <- "0"

    PC002002 <- header[which(header == "PC002002") + 1] |> as.numeric()
    CDELT2 <- header[which(header == "CDELT2") + 1] |> as.numeric()
    CD2_2 <- (PC002002 * CDELT2) |> sprintf(fmt = "%.14e")

    start_i <- which(header == "CDELT1") - 1
    end_i <- length(header)

    # header1 <- header[1:start_i]
    # header2 <- header[start_i:end_i]

    header <- c(
      header,
      "CD1_1", CD1_1,
      "CD1_2", CD1_2,
      "CD2_1", CD2_1,
      "CD2_2", CD2_2
    )
    
    return(header)
  }
}
```

### Plot the image guidance

It is example how to make a guidance plot. You should wrap it in your function for best practice.

```{r, fig.width=5, fig.height=5}
oma_old <- par('oma')
mar_old <- par('mar')
par(oma = c(0, 0, 0, 0), mar = c(0, 0, 0, 0))
# Convert source coords_uma from (RA, DEC) to image coords (X,Y)
src <- celestial::radec2xy(
    RA = coords_uma$ra,
    Dec = coords_uma$dec,
    header = fix_header(fits_obj$hdr)
  )

# Plot image
magicaxis::magimage(
    fits_obj$imDat,
    asp = 1,
    flip = T,
    stretch = 'log',
    type = 'quan',
    lo=0.6,
    hi = 0.99,,
    grid.lwd = 0,
    axes=F)

# Add compass to image
magicaxis::magimageWCSCompass(header = fix_header(fits_obj$hdr))

# Add red circle around our source 
points(x = src[1], 
         y = src[2], 
         cex = 2, 
         col = "red", 
         lwd = 1)

# Add arrow to point out on our source
arrows(x0 = src[1],
         y0 = src[2] + 50,
         x1 = src[1],
         y1 = src[2]+2.5,
         length = .1,
         lwd = 1.5,
         col = 'red')

# Add text to picture
text(x = ncol(fits_obj$imDat)/2,
       y = nrow(fits_obj$imDat)-50,
       label = 'KQ Uma')
par(oma = oma_old, mar = mar_old)
```

